Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-05-12 paper.qmd
Updated Figure 3

start_pt <- all_centroids_df_temp |> 
  filter(hexID == 1)
d_rect <- tibble(x1min = 0, 
                 x1max = 1,
                 x2min = 0,
                 x2max = 1.6)

>>>>

start_pt <- all_centroids_df_temp |> 
  filter(hexID == 1)
d_rect <- tibble(x1min = 0, 
                 x1max = 1,
                 x2min = 0,
                 x2max = diff(algo_obj_two_curvy$nldr_obj$lim2)/diff(algo_obj_two_curvy$nldr_obj$lim1))
